\section{Conclusion}
\label{sec:conclusion}

As large language models transition from isolated completion engines to the cognitive cores of stateful, multi-step agentic systems, the reliability requirements placed on the underlying serving infrastructure must mature in tandem. The current industry standard of stateless failover routing solves the problem of API availability but creates a pernicious vulnerability: the silent destruction of conversational continuity. 

In this work, we have formalized conversational continuity as a measurable operational property, distinct from simple availability. We proposed the Continuity Preservation Rate (CPR) and Continuity Latency Overhead (CLO) metrics to rigorously quantify this property. Through our empirical evaluation of $N=750$ provider failover events, we demonstrated that a History-Forwarding proxy architecture successfully preserves complete conversational context with a 99.20\% CPR, resolving the continuity gap without imposing prohibitive latency overhead. Furthermore, by evaluating this mechanism under production-scale concurrency ($C=100$), we identified two severe systems-level vulnerabilities---concurrency-driven state corruption and the failover retry storm---demonstrating that robust LLM orchestration is fundamentally a distributed systems problem requiring explicit concurrency control and backoff-aware retry protocols.

To accelerate further research in this domain, we have open-sourced our entire evaluation pipeline, including the synthetic multi-turn dataset, the deterministic fault injector, the proxy architecture, and the automated LLM-as-judge scoring harness. We invite the research and engineering community to build upon \textit{continuity-bench} to evaluate novel routing algorithms, explore cross-provider context compression techniques, and ensure that the next generation of AI infrastructure prioritizes not just the survival of the request, but the continuity of the conversation.
